Model details

### 2023-09-13 notebook/analysis-issue.qmd
Switch to native pipe

```{r plot-pred-discrete-continuous-local, message=FALSE, fig.width=6, fig.height=6}
preds_issue_plot <- preds_issue |> 
  unnest(preds) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) %>% 
  group_by(outcome, work_field_code1, draw) %>% 
  summarize(count = n()) |> 
  group_by(work_field_code1, draw) |> 
  mutate(prop = count / sum(count))

>>>>

```{r plot-pred-discrete-continuous-local, message=FALSE, fig.width=6, fig.height=6}
preds_issue_plot <- preds_issue |> 
  unnest(preds) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) |> 
  group_by(outcome, work_field_code1, draw) |> 
  summarize(count = n()) |> 
  group_by(work_field_code1, draw) |> 
  mutate(prop = count / sum(count))

### 2023-09-13 notebook/analysis-local.qmd
Switch to native pipe

```{r plot-pred-discrete-continuous-local, message=FALSE}
preds_local_plot <- preds_local |> 
  unnest(preds) |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) %>% 
  group_by(outcome, local_connect, draw) %>% 
  summarize(count = n()) |> 
  group_by(local_connect) |> 
  mutate(prop = count / sum(count) * 100)

>>>>

```{r plot-pred-discrete-continuous-local, message=FALSE}
preds_local_plot <- preds_local |> 
  unnest(preds) |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) |> 
  group_by(outcome, local_connect, draw) |> 
  summarize(count = n()) |> 
  group_by(local_connect) |> 
  mutate(prop = count / sum(count) * 100)

### 2023-09-13 notebook/analysis-timing.qmd
Switch to native pipe

```{r plot-epred-timing-lineribbon}
epreds %>% 
  ggplot(aes(x = years_since_law, y = .epred)) +
  scale_x_reverse() +
  scale_y_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces")) +
  labs(x = "Years since law took effect (2017)", 
       y = "Expected proportion of provinces") +
  stat_lineribbon(alpha = 0.35, fill = clrs[7], color = clrs[7]) +
  theme_ongo() +
  theme(axis.title.y.right = element_text(hjust = 1, margin = margin(l = 10), angle = 90))
```

```{r plot-pred-discrete-continuous-timing, message=FALSE}
preds_timing_plot <- preds_timing |> 
  unnest(preds) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) %>% 
  group_by(outcome, years_since_law, draw) %>% 
  summarize(count = n()) |> 
  group_by(years_since_law) |> 
  mutate(prop = count / sum(count) * 100)

>>>>

```{r plot-epred-timing-lineribbon}
epreds |> 
  ggplot(aes(x = years_since_law, y = .epred)) +
  scale_x_reverse() +
  scale_y_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces")) +
  labs(x = "Years since law took effect (2017)", 
       y = "Expected proportion of provinces") +
  stat_lineribbon(alpha = 0.35, fill = clrs[7], color = clrs[7]) +
  theme_ongo() +
  theme(axis.title.y.right = element_text(hjust = 1, margin = margin(l = 10), angle = 90))
```

```{r plot-pred-discrete-continuous-timing, message=FALSE}
preds_timing_plot <- preds_timing |> 
  unnest(preds) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) |> 
  group_by(outcome, years_since_law, draw) |>
  summarize(count = n()) |> 
  group_by(years_since_law) |> 
  mutate(prop = count / sum(count) * 100)

### 2023-09-13 notebook/model-details.qmd
Switch to native pipe

posterior_categories <- full_posterior %>% 
  ungroup() %>% 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1",
    .prediction > 0 & .prediction < 1 ~ "1–32",
    .prediction == 1 ~ "32"
  )) %>% 
  group_by(outcome, .draw) %>% 
  summarize(count = n()) %>% 
  ungroup()

@@

plot_categories <- posterior_categories %>% 
  ggplot(aes(x = outcome, y = count)) +
  geom_col(data = actual_counts, fill = "grey70") +
  stat_pointinterval() +
  labs(x = NULL, y = "Observed and predicted counts",
       title = "Posterior predictions of discrete and continuous outcomes") +
  coord_cartesian(ylim = c(0, 300)) +
  theme_ongo()

>>>>

posterior_categories <- full_posterior |> 
  ungroup() |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1",
    .prediction > 0 & .prediction < 1 ~ "1–32",
    .prediction == 1 ~ "32"
  )) |> 
  group_by(outcome, .draw) |> 
  summarize(count = n()) |> 
  ungroup()

@@

plot_categories <- posterior_categories |> 
  ggplot(aes(x = outcome, y = count)) +
  geom_col(data = actual_counts, fill = "grey70") +
  stat_pointinterval() +
  labs(x = NULL, y = "Observed and predicted counts",
       title = "Posterior predictions of discrete and continuous outcomes") +
  coord_cartesian(ylim = c(0, 300)) +
  theme_ongo()
